---
title: "Data Pre-processing"
author: 'Script written by Emiko Muraki and adapted by Veronica Diveica'
output:
  word_document: default
---

```{r setup,include = FALSE}
#Load packages
library(plyr)
library(tidyverse)

# set chunk options
knitr::opts_chunk$set(include = FALSE)
```


```{r data, include=FALSE}

#Create path to raw data
path <- "Data/Raw"

#Create path to export results out
path_out <- "Data/Preprocessed"

#Load all csv files in data directory
data_files <- list.files(path = path, pattern = "*.csv", full.names = TRUE)
data <- ldply(data_files, read_csv)

# Tidy dataframe
sct <- data %>% 
  select(Emb_practice.thisIndex, embResp.keys, embResp.corr, embResp.rt, Word,  condition, Socialness, Dom_PoS_SUBTLEX, Concreteness, Cresp, participant, Embody.thisIndex) %>% 
  filter(condition %in% c("A1_B1", "A1_B2", "A2_B1", "A2_B2")) %>%
  filter(is.na(Emb_practice.thisIndex)) %>%
  rename("PoS" = "Dom_PoS_SUBTLEX", "Socialness_Rating" = "Socialness") %>%
  mutate(Socialness = case_when(condition == "A1_B1" ~ "Nonsocial", condition == "A2_B1" ~ "Social", 
                                condition == "A1_B2" ~ "Nonsocial", condition == "A2_B2" ~ "Social"))  # add info about stimuli categories

```


```{r ppt accuracy, include=FALSE}

# CHECK PARTICIPANTS' ACCURACY
# calculate accuracy threshold
binom.test(159, 268, 0.5, alternative = "greater") # p = 0.01347
acc_threshold <- binom.test(160, 268, 0.5, alternative = "greater") # p = 0.0009 Prob of success 0.597
acc_threshold <- as.numeric(acc_threshold$estimate)

#Calculate participant accuracy stats
participant_acc <- sct %>% 
  group_by(participant) %>% 
  summarise(pptAcc = sum(embResp.corr)/268) # get amount correct out of total trials

#Get list of participants with accuracy less than threshold
accuracy_exclusions <- participant_acc %>% 
  filter(pptAcc < acc_threshold) 

# Save list of participants excluded due to below chance accuracy
write.csv(accuracy_exclusions, file.path(path_out, file = "Participant_Accuracy_Exclusions.csv"), row.names = FALSE)

#Filter data to exclude participants with low accuracy
"%notin%" <- Negate("%in%") #Create notin operator
sct_lowaccremove <- sct %>% 
  filter(participant %notin% accuracy_exclusions$participant)

```

```{r item accuracy, include=FALSE}

## CHECK ITEM-LEVEL ACCURACY
#Calculate item accuracy stats
item_acc <- sct_lowaccremove %>% 
  group_by(Word) %>% 
  summarise(itemAcc = sum(embResp.corr)/nrow(participant_acc))

#Get list of items with accuracy less than threshold
item_exclusions <- item_acc %>%
  filter(itemAcc < 0.5)

#Save items excluded due to accuracy
write.csv(item_exclusions, file.path(path_out, file = "Item_Exclusions.csv"), row.names = FALSE)

#Filter data to exclude items with low accuracy
sct_lowaccremove_itemremove <- sct_lowaccremove %>%
  filter(Word %notin% item_exclusions$Word)


```

```{r trial outliers, include=FALSE}

## CHECK OUTLIER TRIALS
#Calculate participant response time mean and SD 
participant_resp <- sct_lowaccremove_itemremove %>% 
  group_by(participant) %>% 
  summarise(MeanRT = mean(embResp.rt, na.rm = TRUE), SD = sd(embResp.rt, na.rm = TRUE)) %>% 
  mutate(SD_UL = MeanRT + 3*SD) # calculate participant-level upper threshold

# Filter data to exclude outlier trials
sct_final <- left_join(sct_lowaccremove_itemremove, participant_resp, by = "participant") %>%
  mutate(trial_exclude = ifelse(embResp.rt > SD_UL | embResp.rt < 0.25 , 1, 0)) %>%
  filter(trial_exclude == 0  | is.na(trial_exclude)) %>%
  select(participant, Word, embResp.corr, embResp.rt, PoS, Socialness, Concreteness)

```


```{r clean data, include=FALSE}

# save clean data
colnames(sct_final)[3:4] <- c("ACC", "RT")
write_csv(sct_final, file.path(path_out, file = "Data_clean.csv"))

# calculate data loss
excluded_obs <- nrow(sct)-nrow(sct_final) # all
excluded_verb <- nrow(sct%>%filter(PoS=="Verb"))-nrow(sct_final%>%filter(PoS=="Verb")) # experimental only

```

```{r demographics}

# load sample demographics data
dmg <- read_csv("Data/Demographics.csv")

# clean
dmg <- dmg %>% 
  slice_tail(n = nrow(dmg)-2) %>%
  filter(ResponseId %in% sct_final$participant) %>%
  select(ResponseId, D1, D2, Q6) %>%
  mutate(across(2:3, as.numeric))
colnames(dmg)[2:4] <- c("Age", "Education", "Gender") 

```

**Participants**
The participants were recruited via the online platform Prolific (www.prolific.co). Responders were restricted to those who had a 100% approval rate on Prolific and self-reported being fluent in English and having no language disorders. Participants completed the study in 20 minutes on average and were compensated with GBP £4. We collected data from a sample of `r nrow(dmg)` participants, with ages ranging from `r min(dmg$Age)` to `r max(dmg$Age)` (*M* = `r round(mean(dmg$Age), 2)`, *SD* = `r round(sd(dmg$Age), 2)`). Of the participants, `r nrow(filter(dmg, Gender == "Woman"))` were female, `r nrow(filter(dmg, Gender == "Man"))` male, `r nrow(filter(dmg, Gender == "Non-binary"))` non-binary and `r nrow(filter(dmg, Gender == "Prefer not to answer"))` unknown. On average, participants completed `r round(mean(dmg$Education), 2)` years (*SD* = `r round(sd(dmg$Education), 2)`) of formal education. 

**Data Cleaning**
We collected a total of `r nrow(sct)` observations. We excluded data from `r nrow(accuracy_exclusions)` participants with below-chance accuracy. In addition, `r nrow(item_exclusions)` words were excluded because less than 50% of participants provided correct responses. Finally, `r excluded_verb` of the experimental trials (`r round(excluded_verb*100/nrow(sct%>%filter(PoS=="Verb")), 2)`%) were identified as RT outliers and were excluded from the analyses. Thus, the analyses reported are based on `r nrow(filter(sct_final, PoS == "Verb"))` experimental observations, out of which `r nrow(filter(sct_final, PoS == "Verb", ACC == 1))` are correct trials.


 
**Session Info**
```{r session info, include = TRUE}

xfun::session_info()

```

