---
title: "Study 3 - Data Analysis"
author: "Veronica Diveica"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
---

```{r setup, include = FALSE}
# set knitting options
knitr::opts_chunk$set(include = FALSE, echo = FALSE, message = FALSE, warning=FALSE)

# load relevant packages
library(plyr) # data wrangling
library(tidyverse) # data wrangling
library(sjPlot) # model summary tables & figures
library(lmerTest) # lmm p vals
library(lme4) # lmm
library(afex) # lmm likelihood ratio tests
library(interactions) # visualize results of interaction terms
library(ggprism) # figure theme
library(rstanarm) # bayesian analysis
library(bayestestR) # bayesian analysis

# Load data
data <- read_csv("Data/Preprocessed/Data_clean.csv")
```


# R Session Information
```{r session info, include = TRUE}
sessionInfo()
```

# The effect of socialness on reaction times (log transformed)

```{r logRT}

# filter, factorize, scale
data_RT <- data %>% 
  filter(ACC == 1 & PoS == "Noun") %>% # remove inaccurate and verb trials
  mutate(Concreteness = scale(Concreteness)) %>% # standardize concreteness
  mutate(across(c(participant, Word, Socialness), as.factor)) %>% # factorize variables
  mutate("logRT" = log10(RT)) %>% # log transform RTs
  mutate(Socialness_coded = ifelse(Socialness == "Social", 0.5, -0.5))
contrasts(data_RT$Socialness) <- c(-0.5, 0.5) # set condition to be effects coded: Social = .5; Non-social = -.5

# fit maximal model
# m1 <- lmer(logRT ~ Socialness*Concreteness + (1 + Socialness*Concreteness|participant) + (1|Word), data = data_RT)

# Identify optimal random effects structure

# 1. Run PCA on random effects of maximal model to  determine the number of random effects that could be specified (i.e., the number of components explaining >1% of variance) while achieving model identification.
# pca_model1 <- rePCA(m1)
# summary(pca_model1) # PCA indicates that the maximal model is overparameterized

# 2. Perform iterative reduction of model complexity to arrive at parsimonious model.
# 2.1. check whether zero-correlation parameter model is overfitted
#m2 <- lmer_alt(logRT ~ Socialness*Concreteness + (1 + Socialness*Concreteness||participant) + (1|Word), data = data_RT)

# model does not converge, use different optimizer
m2 <- lmer_alt(logRT ~ Socialness*Concreteness + (1 + Socialness*Concreteness||participant) + (1|Word),
            data = data_RT,
            control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=100000)))

pca_model2 <- rePCA(m2)
summary(pca_model2) # PCA indicates identified model, making m2 the optimal model

# fit model
model <- m2
estimates_RT <- get_model_data(model, type = "std")

# get results summary
sum_model <- summary(model)
sum_model

# fit best model using Socialness_coded variable for input to interaction plot - see below
model_interact <- lmer(logRT ~ Socialness_coded*Concreteness + (1 + Socialness_coded*Concreteness||participant) + (1|Word), data = data_RT)

# ROPE analysis

# set.seed(19711)
# generic_prior <- normal(location = c(0,0,0), scale = c(2.5,2.5,2.5), autoscale = TRUE)
#
# bm_log_rt <- stan_glmer(logRT ~ Socialness*Concreteness + (1 + Socialness*Concreteness||participant) + (1|Word),
#                         data = data_RT, prior = generic_prior, iter = 6000) 
# 
# save(bm_log_rt, file = "Output/ROPE_logRT_model.RData") # save analysis results to save time when re-running script
load("Output/ROPE_logRT_model.RData") # load saved data 

percentage_in_rope_log_rt <- rope(bm_log_rt, ci = 0.95) # extract percentage most probable estimates in ROPE
pd_log_rt <- p_direction(bm_log_rt) # extract probability of direction

```

## LMM Results

Iterative procedure suggests modelling random intercept and slopes per participant, without slope/intercept correlations. Model with optimal random effects structure: logRT ~ Socialness* Concreteness + (1 + Socialness*Concreteness||participant) + (1|Word)  

```{r logRT results2}

# plot the interaction using item-level means

dat <- data_RT %>% 
  group_by(Word) %>%
  summarize(Item_meanRT = mean(RT))

dat <- left_join(dat, data)
  
fig1 <- ggplot(dat, aes(x = Concreteness, y = Item_meanRT, colour = Socialness)) +
  geom_point(aes(shape = Socialness), size = 2, alpha = 1/50, stroke = 1) +
  geom_smooth(method=lm)  +
  theme_prism() +
  scale_shape_manual(values=c(1, 2))+
  scale_colour_manual(values = c("#79ad41",  "#d7aca1")) +
  ylab("Word Mean RT (s)") +
  scale_x_continuous(limits = c(1.5, 4.5), breaks = c(1.5, 2.5, 3.5, 4.5)) +
  theme(legend.position = "none") +
  scale_y_continuous(limits = c(0.8, 1.8), breaks = c(0.8, 1, 1.2, 1.4, 1.6, 1.8))

ggsave("Figures/RT_effects_item.png", width = 4, height = 4)

```

```{r logRT results3, include = TRUE}

# results table 
sjPlot::tab_model(model, show.df = TRUE, df.method = "satterthwaite", 
                  show.obs = FALSE, show.stat = TRUE, show.r2 = TRUE, show.ngroups = FALSE)

# plot results
# standardized coefficients
sjPlot::plot_model(model, type = "std", show.values = TRUE, show.p = TRUE) 
# plot predicted values (marginal effects) for main effects
sjPlot::plot_model(model,type="pred")
# visualize the interaction
interact_plot(model_interact, pred = Socialness_coded, modx = Concreteness, x.label = "Socialness", pred.labels = c("Non-social", "Social"))

# visualize the interaction using item-level means

fig1

```

### Check Assumptions

```{r logRT results1, include = TRUE, fig.height=12}

# check assumptions
performance::check_model(model)

```

## Bayesian ROPE analysis

The Bayesian analyses estimated that `r round(percentage_in_rope_log_rt[2, 5]*100, digits = 2)`% of the HDI for socialness (`r round(pd_log_rt[2, 2]*100, digits = 2)`% PD), `r round(percentage_in_rope_log_rt[3, 5]*100, digits = 2)`% for concreteness (`r round(pd_log_rt[3, 2]*100, digits = 2)`% PD), and `r round(percentage_in_rope_log_rt[4, 5]*100, digits = 2)`% for the interaction (`r round(pd_log_rt[4, 2]*100, digits = 2)`% PD), fell within the ROPE (`r round(percentage_in_rope_log_rt[1, 3], digits = 3)`-`r round(percentage_in_rope_log_rt[1, 4], digits = 3)`).


```{r rope log rt, include = TRUE}

plot(pd_log_rt) + theme_prism()

plot(percentage_in_rope_log_rt) + theme_prism()
```

# The effect of socialness on accuracy

```{r Accuracy}

data_ACC <- data %>% 
  filter(PoS == "Noun") %>% # remove verb trials
  mutate(Concreteness = scale(Concreteness)) %>% # standardize concreteness
  mutate(across(c(participant, Word, Socialness, ACC), as.factor)) %>% # factorize variables
  mutate(Socialness_coded = ifelse(Socialness == "Social", 0.5, -0.5))
contrasts(data_ACC$Socialness) <- c(-0.5, 0.5) # set condition to be effects coded: Social = .5; Non-social = -.5

# fit maximal model
# m1 <- glmer(ACC ~ Socialness*Concreteness + (1 + Socialness*Concreteness|participant) + (1|Word),
#             data = data_ACC,
#             family = 'binomial')

# model does not converge, use different optimizer
#all_fit(m1) # bobyqa

# m1 <- glmer(ACC ~ Socialness*Concreteness + (1 + Socialness*Concreteness|participant) + (1|Word),
#             data = data_ACC,
#             family = 'binomial',
#             control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=100000)))
# save(m1, file = "Output/Binomial_ACC.RData")
load("Output/Binomial_ACC.RData")

## Identify optimal random effects structure

# 1. Run PCA on random effects of maximal model to  determine the number of random effects that could be specified (i.e., the number of components explaining >1% of variance) while achieving model identification.
pca_model1 <- rePCA(m1)
summary(pca_model1) # PCA indicates idetified model, making m1 the optimal model

# fit model
model <- m1
estimates_ACC <- get_model_data(model, type = "std")

# get results summary
sum_model <- summary(model)
sum_model

# fit best model using Socialness_coded variable for input to interaction plot - see below
model_interact <- glmer(ACC ~ Socialness_coded*Concreteness + (1 + Socialness_coded*Concreteness|participant) + (1|Word), data = data_ACC, family = 'binomial', control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=100000)))

# ROPE analysis
# bm_acc <- stan_glmer(ACC ~ Socialness*Concreteness + (1 + Socialness*Concreteness|participant) + (1|Word),
#             data = data_ACC,
#             prior = generic_prior,
#             family = 'binomial',
#             iter = 6000)
# save(bm_acc, file = "Output/ROPE_ACC_model.RData")
load("Output/ROPE_ACC_model.RData")

percentage_in_rope_acc <- rope(bm_acc, ci = 0.95)
pd_acc <- p_direction(bm_acc)


```

Iterative procedure suggests modelling random intercept and slopes per participant. Model with optimal random effects structure: Accuracy ~ Socialness^Concreteness + (1 + Socialness*Concreteness|participant) + (1|Word)  

## LMM

```{r accuracy results2}
# plot the interaction using item-level means
dat <- data %>% 
  filter(PoS == "Noun") %>% # remove verb trials
  group_by(Word) %>%
  summarise(Item_meanACC = mean(ACC)*100) %>%
  mutate(Item_meanERR = 100 - Item_meanACC)

dat <- left_join(dat, data)
  
fig2 <- ggplot(dat, aes(x = Concreteness, y = Item_meanERR, colour = Socialness)) +
  geom_point(aes(shape = Socialness), size = 2, alpha = 1/50, stroke = 1) +
  geom_smooth(method=lm)  +
  theme_prism() +
  scale_shape_manual(values=c(1, 2))+
  scale_colour_manual(values = c("#79ad41",  "#d7aca1")) +
  ylab("Word Incorrect Responses (%)") +
  scale_x_continuous(limits = c(1.5, 4.5), breaks = c(1.5, 2.5, 3.5, 4.5)) +
  theme(legend.position = "none")

ggsave("Figures/ACC_effects_item.png", width = 4, height = 4)

```


```{r accuracy results3, include = TRUE}

# results table 
sjPlot::tab_model(model, show.obs = FALSE, show.stat = TRUE, show.r2 = TRUE, show.ngroups = FALSE)

# plot results
# standardized coefficients
sjPlot::plot_model(model, type = "std", show.values = TRUE, show.p = TRUE) 
# plot predicted values (marginal effects) for main effects
sjPlot::plot_model(model,type="pred")
# visualize the interaction
interact_plot(model_interact, pred = Socialness_coded, modx = Concreteness, x.label = "Socialness", pred.labels = c("Non-social", "Social")) + theme_prism()
# visualize the interaction using item-level means
fig2

```

### Check Assumptions
```{r accuracy results1, include = TRUE} 

# check assumptions
sjPlot::plot_model(model,type="diag")
```

## ROPE Analysis

The Bayesian analyses estimated that `r round(percentage_in_rope_acc[2, 5]*100, digits = 2)`% of the HDI for socialness (`r round(pd_acc[2, 2]*100, digits = 2)`% PD), `r round(percentage_in_rope_acc[3, 5]*100, digits = 2)`% for concreteness (`r round(pd_acc[3, 2]*100, digits = 2)`% PD), and `r round(percentage_in_rope_acc[4, 5]*100, digits = 2)`% for the interaction (`r round(pd_acc[4, 2]*100, digits = 2)`% PD), fell within the ROPE (`r round(percentage_in_rope_acc[1, 3], digits = 3)`-`r round(percentage_in_rope_acc[1, 4], digits = 3)`).


```{r rope acc, include = TRUE, warning=FALSE, message=FALSE}
plot(pd_acc) + theme_prism()

plot(percentage_in_rope_acc) + theme_prism()
```


# The effect of socialness on raw RTs

```{r raw RT}

## fit maximal model
# m1 <- lmer(RT ~ Socialness*Concreteness + (1 + Socialness*Concreteness|participant) + (1|Word), data = data_RT)

## Identify optimal random effects structure

# 1. Run PCA on random effects of maximal model to  determine the number of random effects that could be specified (i.e., the number of components explaining >1% of variance) while achieving model identification.
# pca_model1 <- rePCA(m1)
# summary(pca_model1) # PCA indicates that the maximal model is overparameterized

# 2. Perform iterative reduction of model complexity to arrive at parsimonious model.
# 2.1. check whether zero-correlation parameter model is overfitted
m2 <- lmer_alt(RT ~ Socialness*Concreteness + (1 + Socialness*Concreteness||participant) + (1|Word), data = data_RT)
pca_model2 <- rePCA(m2)
summary(pca_model2) # PCA indicates identified model, making m2 the optimal model

# fit model
model <- m2

sum_model <- summary(model)
sum_model

model_interact <- lmer_alt(RT ~ Socialness_coded*Concreteness + (1 + Socialness_coded*Concreteness||participant) + (1|Word), data = data_RT)
# 
# ROPE analysis # HERE need to run

# bm_rt <- stan_glmer(RT ~ Socialness*Concreteness + (1 + Socialness*Concreteness||participant) + (1|Word), data = data_RT, prior = generic_prior, iter = 6000)
# 
# save(bm_rt, file = "Output/ROPE_RT_model.RData")
# load("Output/ROPE_RT_model.RData")
# 
# percentage_in_rope_rt <- rope(bm_rt, ci = 0.95)
# pd_rt <- p_direction(bm_rt)

```

## LMM

Iterative procedure suggests modelling random intercept and slopes per participant, without slope/intercept correlations. Model with optimal random effects structure: RT ~ Socialness* Concreteness + (1 + Socialness*Concreteness||participant) + (1|Word)


```{r RT results2, include=TRUE}

# results table
tab_model(model, df.method = "satterthwaite")
# plot results
# standardized coefficients
plot_model(model, type = "std", show.values = TRUE, show.p = TRUE)
# plot predicted values (marginal effects) for main effects
plot_model(model,type="pred")
# visualize the interaction
interact_plot(model_interact, pred = Socialness_coded, modx = Concreteness, x.label = "Socialness", pred.labels = c("Non-social", "Social"))

```

### Check Assumptions

```{r RT results1, include = TRUE, fig.height=12, warning=FALSE, message=FALSE}

# check assumptions
performance::check_model(model) # assumptions violated

```

<!-- ## ROPE Analysis -->

<!-- ```{r rope rt, include = TRUE, warning=FALSE, message=FALSE} -->

<!-- plot(pd_rt) + theme_prism() -->

<!-- plot(percentage_in_rope_rt) + theme_prism() -->
<!-- ``` -->

# Explore socialness by PoS, controlling for concreteness

```{r pos}

# prepare data
dat <- read_csv("Data/Other/Word_properties.csv")
pos_dat <- read_csv("Data/Other/SUBTLEX-US frequency list with PoS and Zipf information.csv")
pos_dat <- pos_dat %>% select(Word, Dom_PoS_SUBTLEX)
pos <- left_join(dat, pos_dat) 
pos <- pos %>% 
  filter(Dom_PoS_SUBTLEX == "Noun" | Dom_PoS_SUBTLEX == "Verb") %>%
  mutate(`Part of Speech` = as.factor(Dom_PoS_SUBTLEX))
contrasts(pos$`Part of Speech`) <- c(-0.5, 0.5) # set condition to be effects coded

# run linear model
model_pos <- lm(Socialness ~ 1 + `Part of Speech` + Concreteness, data = pos)

```

```{r pos viz, include = TRUE, fig.height=2, fig.width=2}
# summary table
sjPlot::tab_model(model_pos, show.df = TRUE, 
                  show.obs = FALSE, show.stat = TRUE, show.r2 = TRUE, show.ngroups = FALSE)
# visualize 
fig3 <- sjPlot::plot_model(model_pos, type="pred", terms = c("Part of Speech"))


print(fig3)
dev.copy(jpeg, filename = "Figures/Socialness_by_PoS.png")
dev.off()
```